We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-01 paper/paper.tex
+1 paragraph

\subsection{$c/a$ axis ratio}

>>>>

\subsection{$c/a$ axis ratio}
Figure \ref{fig:scatter_ca_ratio} shows the results for the minor to
major axis ratio. 
Corresponding in the ELVIS data are in the appendix in Figure
\ref{fig:scatter_elvis}.

The left panel shows the results for the LG compared against its
spherically randomized version.
As expected the $c/a$ ratio in the MW is significantly lower as the
measured values for spherical distributions. 
On the other hand the ratio for M31 is lower than the mean of the
spherical values but still well within its variance.
In contrast to the results for the plane width, this time the
randomized values have symmetrical expectations between the two
galaxies.

The midle panel
